---
title: "Automate PCMH QA Process"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Automate PCMH QA Process}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pcmh)
```

This document outlines the process for QA'ing one of the three PCMH report types:
  (2020 PCMH, 2020 Shared Savings, 2021 PCMH). The process is the same for each 
  report but the internal data you reference will depend on which report type you
  are QA'ing.
  
## Internal Data

You will have to reference one of pcmh20_crosswalk, pool20_crosswalk, or
  pcmh21_crosswalk when QA'ing 2020 PCMH, 2020 Shared Savings, or 2021 PCMH
  when QA'ing each report type, respectively.

Each of the internal data sets will look like:

```{r}
dplyr::glimpse(pcmh:::pcmh20_crosswalk)
```

and we will use them to compare the data we extract from the PCMH reports to the
  data gathered by Riley's team.

Each of the data sets have extra variables that currently aren't used in QA as
  of 9/14/2021. So you first must subset the specific data set to remove these
  before QA begins. For this example, we are assuming report type is 2021 PCMH.
  
```{r}
crosswalk <-
  pcmh:::pcmh21_crosswalk[which(!is.na(pcmh:::pcmh21_crosswalk$variable) &
                              !is.na(pcmh:::pcmh21_crosswalk$x) &
                              !is.na(pcmh:::pcmh21_crosswalk$x_min) &
                              !is.na(pcmh:::pcmh21_crosswalk$x_max) &
                              !is.na(pcmh:::pcmh21_crosswalk$y) &
                              !is.na(pcmh:::pcmh21_crosswalk$y_min) &
                              !is.na(pcmh:::pcmh21_crosswalk$y_max)), ]
```

## Read in data

Next you must read in both the .pdf reports and the data from Riley's team to 
  compare.
  
### Metric Data

First, you call the import_metric_data function to read in and clean the data 
  from Riley's team. You will need to pass it the filepath to the directory the
  data is in, a regular expression to select the specific data for the quarter, 
  and col_types = c(.default = "c") to specify each column is read in as character
  type.
  
```{r}
metric_data <-
  pcmh::import_metric_data(
    "U:/AHCPII/Episodes of Care/Qrtly Reports/SAS team QA/Individual folders/Joseph/projects/pcmh_qa/data",
    .regexp = "report_pcmh_2021q3_21",
    col_types = c(.default = "c")
  )
```

The metric data will differ depending on report type but will be simmilar to:

```{r}
head(metric_data)
```

### PCMH reports

Next, you will need to read in the .pdf reports. To do this more quickly, we will
  use the furrr package.
  

```{r}
future::plan(future::multisession)

reports <- 
  pcmh::import_pdf_data("U:/AR_reports/PCMH/Q32021_PCMH_2021_09072021_FINAL/Original",
                        regexp = ".pdf")
```


## Generating Output

Once the reports and metric data have been read in, we can use pcmh::generate_detail
  and pcmh::generate_summary functions to create the output.

### Detail

Again we can use the furrr package to help sped up the process.

```{r}
detail <-
  furrr::future_map_dfr(reports,
          ~ {
            report <- .x
            furrr::future_map_dfr(
              1:nrow(crosswalk),
              ~ pcmh::generate_detail(report,
                                      metric_data,
                                      crosswalk[.,])
            )
          })
```

### Summary 

```{r}
summary <- 
  furrr::future_map_dfr(detail$prvdr_num |>
            unique(),
          ~ pcmh::generate_summary(detail, .))
```

At this point the Summary and Detail pages should look similar to

```{r}
head(summary)
head(detail)
```

